Combining global tree cover loss data with historical national forest cover maps to look at six decades of deforestation and forest fragmentation in Madagascar

### 2018-01-18 manuscript/manuscript.Rnw
Cover letter

Because of the large unclassified area (3.3 million ha) in 1973, the
annual deforestation areas and rates for the two periods 1953-1973 and
1973-1990 are only partial estimates computed on the basis of the
available forest extent. Area and rate estimates are produced at the
national scale and for the four forest ecosystems present in
Madagascar: moist forest in the East, dry forest in the West, spiny
forest in the South, and mangroves on the Western coast
(Fig.~\ref{fig:ecoregion}). To define the forest domains, we used a
map from the MEFT (\emph{``Ministère de l'Environnement et des Forêts
  à Madagascar''}) with the boundaries of the four ecoregions in
Madagascar. Ecoregions were defined on the basis of climatic and
vegetation criteria using the climate classification by
\citet{Cornet1974} and the vegetation classification from the 1996
IEFN national forest inventory \citep{IEFN1996}. Because mangrove
forests are highly dynamic ecosystems that can expand or contract on
decadal scales depending on changes in environmental factors
\citep{Armitage2015}, a fixed delimitation of the mangrove ecoregion
on six decades might not be fully appropriate. As a consequence, our
estimates of the forest cover and deforestation rates for mangroves in
Madagascar must be considered with this limitation.

@@

The authors thank Jean-François Bastin for useful comments on a previous
version of the manuscript and Peter Vogt for useful advices on which
metric to use to estimate forest fragmentation. This study is part of
the Cirad's BioSceneMada project (\url{https://bioscenemada.cirad.fr})
and the Joint Research Center's ReCaREDD project
(\url{http://forobs.jrc.ec.europa.eu/recaredd}). The BioSceneMada
project is funded by FRB (Fondation pour la Recherche sur la
Biodiversité) and the FFEM (Fond Français pour l'Environnement
Mondial) under the project agreement AAP-SCEN-2013 I. The ReCaREDD
project is funded by the European Commission. The authors declare that there are no conflicts of interest related to this article.

@@

    \caption{\textbf{Ecoregions and forest types in Madagascar.}
      Madagascar can be divided into four climatic ecoregions with
      four forest types: the moist forest in the East (green), the dry
      forest in the West (orange), the spiny forest in the South
      (red), and the mangroves on the West coast (blue). Ecoregions
      were defined following climatic \citep{Cornet1974} and
      vegetation \citep{IEFN1996} criteria. The dark grey areas
      represent the remaining natural forest cover for the year 2014.}

>>>>

Because of the large unclassified area (3.3 million ha) in 1973, the
annual deforestation areas and rates for the two periods 1953-1973 and
1973-1990 are only partial estimates computed on the basis of the
available forest extent. Area and rate estimates are produced at the
national scale and for the four forest types present in
Madagascar: moist forest in the East, dry forest in the West, spiny
forest in the South, and mangroves on the Western coast
(Fig.~\ref{fig:ecoregion}). To define the forest types, we used a
map from the MEFT (\emph{``Ministère de l'Environnement et des Forêts
  à Madagascar''}) with the boundaries of the four ecoregions in
Madagascar. Ecoregions were defined on the basis of climatic and
vegetation criteria using the climate classification by
\citet{Cornet1974} and the vegetation classification from the 1996
IEFN national forest inventory \citep{IEFN1996}. Because mangrove
forests are highly dynamic ecosystems that can expand or contract on
decadal scales depending on changes in environmental factors
\citep{Armitage2015}, a fixed delimitation of the mangrove ecoregion
on six decades might not be fully appropriate. As a consequence, our
estimates of the forest cover and deforestation rates for mangroves in
Madagascar must be considered with this limitation.

@@

The authors thank two anonymous reviewers for useful comments on a previous
version of the manuscript. They also thank Peter Vogt for useful advices on which
metric to use to estimate forest fragmentation. This study is part of
the Cirad's BioSceneMada project (\url{https://bioscenemada.cirad.fr})
and the Joint Research Center's ReCaREDD project
(\url{http://forobs.jrc.ec.europa.eu/recaredd}). The BioSceneMada
project is funded by FRB (Fondation pour la Recherche sur la
Biodiversité) and the FFEM (Fond Français pour l'Environnement
Mondial) under the project agreement AAP-SCEN-2013 I. The ReCaREDD
project is funded by the European Commission. The authors declare that there are no conflicts of interest related to this article.

@@

    \caption{\textbf{Ecoregions and forest types in Madagascar.}
      Madagascar can be divided into four climatic ecoregions with
      four forest types: the moist forest in the East (green), the dry
      forest in the West (orange), the spiny forest in the South
      (red), and the mangroves on the West coast (blue). Ecoregions
      were defined following climatic \citep{Cornet1974} and
      vegetation \citep{IEFN1996} criteria. The dark grey areas
      represent the remaining natural forest cover for the year 2014.
      Forest types are defined on the basis of their appartenance to
      one of the four ecoregions.}
